The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-07-06 manuscript.Rmd
[fix #16] explain how to read upset plots + add refs

```{r compare_database_coverage, fig.cap='Overlap between the regional species list (list), records in iDigBio (idigbio), records in OBIS (obis), and records in BOLD (bold) for the Gulf of Mexico (left) and the Pacific Northwest (right). (\\#fig:database-coverage)', echo=FALSE}
knitr::include_graphics("figures/database_coverage.pdf")
```

@@

To search by geographic area, we obtained the boundaries of the Exclusive Economic Zone for the United States from marineregions.org (mrgid:8456) [@mregions]. For the Pacific Northwest, Kozloff did not specify the exact geographic extent covered by his book. We infered a polygon that encompass part of the Oregon coast to the northern parts of Vancouver island. For the Gulf of Mexico, we used the same geographic area as the one defined in [@Tunnell2009].  These geographic areas were split into squares of 0.2°x0.2° which were used to query the web API of iDigBio and OBIS using the R packages ridigbio and robis respectively. The resulting occurences were then clipped to only include records that fell within the EEZ boundaries.

@@

>>>>

```{r compare_database_coverage, fig.cap='Overlap between the regional species list (list), records in iDigBio (idigbio), records in OBIS (obis), and records in BOLD (bold) for the Gulf of Mexico (left) and the Pacific Northwest (right). This plot is generated using the UpSet technique, which uses a matrix-based layout to represent intersections of set and their sizes. The rows represent the sets, the columns represent the intersections, and each set that is part of the intersection is marked with a black filled circle in the matrix cell. Black lines connect the sets that are part of the intersections. (\\#fig:database-coverage)', echo=FALSE}
knitr::include_graphics("figures/database_coverage.pdf")
```

@@

To search by geographic area, we obtained the boundaries of the Exclusive Economic Zone for the United States from marineregions.org (mrgid:8456) [@mregions]. For the Pacific Northwest, Kozloff did not specify the exact geographic extent covered by his book. We infered a polygon that encompass part of the Oregon coast to the northern parts of Vancouver island. For the Gulf of Mexico, we used the same geographic area as the one defined in [@Tunnell2009] by modifying manually the eastern boundaries of the shape file for the Gulf of Mexico provided by marineregions.org (mrgid:4288). These geographic areas were split into squares of 0.2°x0.2° which were used to query the web API of iDigBio and OBIS using the R packages ridigbio and robis respectively. The resulting occurences were then clipped to only include records that fell within the EEZ boundaries.

@@

Figure \@ref(fig:database-coverage) was generated using the R package UpSetR [@Conway2017] based on the UpSet technique [@Lex2014].
